Spin canonical divisors of log stacky curves

### 2015-06-30 stacky_write_up/spin_cring.tex
rewrite intro stacky defns, also view -> treat

\todo{Peter: I think we need something about odd weight modular 
forms before going right into stacks.}
Following Voight and Zureick-Brown \cite{vzb:stacky}, we generalize 
Petri's theorem in many \todo{Peter: not clear to me that ``many'' 
is a good word to use here.  We mostly generalize in one direction}
directions.

\todo{combine below two paragraphs with the corresponding
near-duplicate part from the background}
If $X$ is a curve, \todo{why do you start with a curve and then
move to a stacky curve? shouldn't it be the opposite order?} then
we say $\sx$ is a {\bf stacky curve} with {\bf coarse space} $X$
and {\bf stacky points} (also called {\bf{fractional points}}) $P_1,
\ldots, P_r$ with {\bf stabilizer orders} $e_1,\ldots, e_r \in \BZ_{
\geq 2}$ if 
\[
	\di \sx = \left(\bigoplus_{P\notin \{P_1,\ldots, P_r\}} \langle 
	P \rangle \right) \oplus \left(\bigoplus_{i = 1}^r \left \langle 
	\frac{1}{e_i}P_i \right \rangle \right) \subseteq \BQ \otimes \di X.
\]

As is done in Voight and Zureick-Brown \cite{vzb:stacky} stacky
curves may be formalized as stacks, but for the purposes of this
paper, it suffices to view $\sx$ as a scheme whose associated
divisor group allows a finite number of stacky points.
\todo{I don't know if this is a good statement to make.  We aren't
really viewing $\sx$ as a scheme.  Rather we're are determining 
information about its canonical rings through knowledge of scheme 
data.}

A {\bf log spin curve} is a triple $(\sx, \Delta, \halfcan)$ where
$\Delta \in \di X$ is an effective divisor and $2\halfcan = K _X +
\Delta + \sum_{i=1}^{r} \subhalf{e_i} P_i.$
The central object of study in this paper is the {\bf log spin
canonical ring} of $(\sx, \Delta, \halfcan)$ is
\begin{align*}
	R(\sx, \Delta, \halfcan) = \bigoplus_{d \geq 0} H^0(\sx, d \halfcan)
\end{align*}

@@

\todo{State for even weight modular forms attributed to VZB.}
\begin{thm}
\label{thm:main}
Let $(\sx, \Delta, \halfcan)$ be a log spin curve over a perfect
field $k$, so that $\sx$ has signature $\sigma = (g; e_1, \ldots,
e_r; \delta)$.

@@

\begin{rem}
In fact, the theorem only needs to assume that the stacky curve
is separably rooted, i.e. the residue field at each stacky point
is separable.
\end{rem}

@@

\ssec{Stacky Curves and Log Spin Canonical Rings}
\label{ssec:stacky-background}
\todo{combine the below chunk with the near-duplicate section
in the introduction}
A \textbf{stacky curve} $\sx$ over a field $k$ is a smooth proper
geometrically-connected Deligne-Mumford stack of dimension $1$ over
$k$ with a dense open subscheme. A stacky curve is \textbf{tame} if
its stabilizers are coprime to char $k$. Throughout this paper,
stacky curves will be assumed to be tame and $k$ will always be
algebraically closed. We also assume that the stacky curves are
separably rooted, i.e. the residue field of each stacky points
is separable. The language of stacks will be omitted in
this paper, as it is sufficient to view stacky curves and related
objects $\sx$ as a scheme whose associated divisor group allows for
a finite number of \textbf{stacky points} which may be viewed
heuristically as ``fractional points''. See Voight and
Zureick-Brown for more thorough treatment of these definitions
\cite[Chapter 5]{vzb:stacky}. \todo{again, not quite viewing as a
scheme}

>>>>

Following Voight and Zureick-Brown \cite{vzb:stacky}, we generalize 
Petri's theorem in the direction of stacky curves equipped with
log divisors. For a stacky curve $\sx$ with coarse space $X$ and
stacky points (also called ``fractional points'') $P_1, \ldots, P_r$
with stabilizer orders $e_1, \ldots, e_r \in \BZ_{\geq 2}$,

\[
	\di \sx = \left(\bigoplus_{P\notin \{P_1,\ldots, P_r\}} \langle 
	P \rangle \right) \oplus \left(\bigoplus_{i = 1}^r \left \langle 
	\frac{1}{e_i}P_i \right \rangle \right) \subseteq \BQ \otimes \di X
\]

Then a {\bf log spin curve} is a triple $(\sx, \Delta, \halfcan)$
where $\Delta \in \di X$ is a log divisor and $2\halfcan = K_X +
\Delta + \sum_{i = 1}^{r} \subhalf{e_i} P_i$.

The central object of study in this paper is the {\bf log spin
canonical ring} of $(\sx, \Delta, \halfcan)$ is
\begin{align*}
	R(\sx, \Delta, \halfcan) = \bigoplus_{d \geq 0} H^0(X, d \halfcan)
\end{align*}

\noindent
A brief overview of stacky curves, log divisors, and log spin
canonical rings and references are given in Subsection
~\ref{ssec:stacky-background}.

%If $X$ is a curve, \todo{why do you start with a curve and then
%move to a stacky curve? shouldn't it be the opposite order?} then
%we say $\sx$ is a {\bf stacky curve} with {\bf coarse space} $X$
%and {\bf stacky points} (also called {\bf{fractional points}}) $P_1,
%\ldots, P_r$ with {\bf stabilizer orders} $e_1,\ldots, e_r \in \BZ_{
%\geq 2}$ if 
%\[
	%\di \sx = \left(\bigoplus_{P\notin \{P_1,\ldots, P_r\}} \langle 
	%P \rangle \right) \oplus \left(\bigoplus_{i = 1}^r \left \langle 
	%\frac{1}{e_i}P_i \right \rangle \right) \subseteq \BQ \otimes \di X
%\]

\begin{rem}
\label{rem:stack-formalism}
As is done in Voight and Zureick-Brown \cite{vzb:stacky} stacky
curves may be formalized as stacks, but for the purposes of this
paper, it suffices to treat $\sx$ as a scheme whose associated
divisor group allows a finite number of stacky points.
\end{rem}

%A {\bf log spin curve} is a triple $(\sx, \Delta, \halfcan)$ where
%$\Delta \in \di X$ is a log divisor and $2\halfcan = K_X +
%\Delta + \sum_{i=1}^{r} \subhalf{e_i} P_i.$
%The central object of study in this paper is the {\bf log spin
%canonical ring} of $(\sx, \Delta, \halfcan)$ is
%\begin{align*}
	%R(\sx, \Delta, \halfcan) = \bigoplus_{d \geq 0} H^0(X, d \halfcan)
%\end{align*}

@@

\begin{thm}
\label{thm:main}
Let $(\sx, \Delta, \halfcan)$ be a log spin curve over a perfect
field $k$, so that $\sx$ has signature $\sigma = (g; e_1, \ldots,
e_r; \delta)$.

@@

\begin{rem}
\label{rem:separably-rooted}
In fact, the theorem only needs to assume that the stacky curve
is separably rooted, i.e. the residue field at each stacky point
is separable.
\end{rem}

@@

\ssec{Stacky Curves and Log Spin Canonical Rings}
\label{ssec:stacky-background}
\todo{combine the below chunk with the near-duplicate section
in the introduction}
A \textbf{stacky curve} $\sx$ over a field $k$ is a smooth proper
geometrically-connected Deligne-Mumford stack of dimension $1$ over
$k$ with a dense open subscheme. A stacky curve is \textbf{tame} if
its stabilizers are coprime to char $k$.

Throughout this paper, stacky curves will be assumed to be tame and
$k$ will always be algebraically closed. We also assume that the
stacky curves are separably rooted, i.e. the residue field of each
stacky points is separable. As noted in Remark
~\ref{rem:stack-formalism}, the language of stacks will be omitted
in this paper, as it is sufficient to treat stacky curves and
related objects $\sx$ as a scheme whose associated divisor group
allows for a finite number of \textbf{stacky points} which may be
viewed heuristically as ``fractional points''. See Voight and
Zureick-Brown for more thorough treatment of these definitions
\cite[Chapter 5]{vzb:stacky}.
